Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/intro.tex
Tidied up intro, made habituation pieces a bit clearer

Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}. With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.

@@

However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen instances of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's withdrawal of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.

We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture on smartphones. Mobile platforms have tried to address the risks by communicating data capture to users as the data is captured. However, many users are habituated to these notifications, because they see them all the time, often for things that they don't care about \cite{felt2012android}.

With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data is captured \cite{denning2014situ}. However, human attention is a finite resource \cite{bohme2011security}, and bombarding users with notifications is likely to be counter-productive as it can lead to user frustration and habituation. Therefore, user concerns need to be investigated so that systems can warn users only about situations they are likely to care about.

The goal of this paper is to gain a better sense of user concerns about wearables. To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,784 Internet users about their perceptions of wearable devices and contribute the following: \\[-0.8cm]

>>>>

Wearable technologies, or ``wearables,'' are a \$700 million industry \cite{cmo} that may see significant growth in the near future: one market research company estimates that 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}. With 20\% of the general population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, wearables are bringing ubiquitous computing to everyday life.

@@

However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen instances of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass apps from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.

We have seen similar privacy \cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues \cite{enck2011study, felt2011survey} related to data capture on smartphones. Mobile platforms have tried to address the risks by communicating data capture to users as the data is captured. However, many users are habituated to these notifications, because they see them all the time, often for things that they do not care about \cite{felt2012android}. Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.

With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data is captured \cite{denning2014situ}. However, the possible data types that these devices will be able to capture is likely to dwarf those currently captured by smartphones. Because human attention is a finite resource \cite{bohme2011security}, bombarding users with notifications for every conceivable data capture is likely to be counter-productive as it can lead to user frustration and habituation. Therefore, user concerns need to be investigated so that systems can warn users only about the situations they are likely to care about.

The goal of this paper is to gain a better sense of users' privacy concerns when interacting with wearable devices, so that future systems can take these concerns into account when designing privacy notifications. To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,782 Internet users about their perceptions of wearable devices and contribute the following: %\\[-0.8cm]
